Software Citation Principles

### 2016-03-22 sc-principles/software-citation-principles.tex
adding tildas

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software, often known as software papers (see \S\ref{sec:software_papers}).
While some journals (e.g., Transactions on Mathematical Software [TOMS], Bioinformatics, F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals
\cite{aas-sofware-papers}. 
Professional societies are in a good position to change their respective communities, as the publishers of journals and conveners of domain-specific conferences; as publishers they can change editorial policies (as AAS has done) and conferences are an opportunity to communicate and discuss these changes with their communities.

In astronomy \& astrophysics: ASCL \cite{ascl}, AAS journals  and the joint
AAS/GitHub workshop \cite{aas-software-index} dedicated to software citation,
indexing and discoverability.

Life sciences/NIH: Software Discovery Index Meeting Report \cite{software-discovery-index} a cross-disciplinary meeting
but with a largely biomedical-focus. Suggested minimal information about software (MIAS) standard. Discusses how a common set of metadata
fields are critical for useful indexing - suggested candidates for this list.

Geosciences: Ontosoft \cite{ontosoft} - A Community Software Commons for the Geosciences. Lots of attention given to the metadata
required to describe, discover and execute research software. NSF geosciences workshop around data lifecycle, management and citation \cite{nsf-geo-data}. This report includes many recommendations for data citation.
\LJHnote{ The Seismological Research Letters, Electronic Seismologists publishes papers on software.} %text needs to be cleaned up LJH%

>>>>

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software, often known as software papers (see \S\ref{sec:software_papers}).
While some journals (e.g., Transactions on Mathematical Software [TOMS], Bioinformatics, F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals~\cite{aas-sofware-papers}. 
Professional societies are in a good position to change their respective communities, as the publishers of journals and conveners of domain-specific conferences; as publishers they can change editorial policies (as AAS has done) and conferences are an opportunity to communicate and discuss these changes with their communities.

In astronomy \& astrophysics: ASCL~\cite{ascl}, AAS journals  and the joint
AAS/GitHub workshop~\cite{aas-software-index} dedicated to software citation,
indexing and discoverability, and the report from a Birds of a Feather session
organized by the ASCL at the Astronomical Data Analysis Software and Systems
(ADASS) XXV conference~\cite{2015arXiv151207919A}.

Life sciences/NIH: Software Discovery Index Meeting Report~\cite{software-discovery-index} a cross-disciplinary meeting
but with a largely biomedical-focus. Suggested minimal information about software (MIAS) standard. Discusses how a common set of metadata
fields are critical for useful indexing - suggested candidates for this list.

Geosciences: Ontosoft~\cite{ontosoft} - A Community Software Commons for the Geosciences. Lots of attention given to the metadata
required to describe, discover and execute research software. NSF geosciences workshop around data lifecycle, management and citation~\cite{nsf-geo-data}. This report includes many recommendations for data citation.
\LJHnote{ The Seismological Research Letters, Electronic Seismologists publishes papers on software.} %text needs to be cleaned up LJH%
